A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-02 paper/paper.Rnw
Add brand information

@@

\paragraph{Overall Accuracy} % Model-wise and class-by-class, w/ confusion matrix
\svp{You need to explain these terms. Your CC was written for statisticians, this paper is for practitioners. You need a MUCH gentler introduction to the idea of accuracy, errors, and ROC curves, as well as a lot more definitions for terms.}
\autoref{fig:roc-code} shows the ROC curve for the full model, and \autoref{fig:auc-code} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for line) to 0.91 (for bowtie and text). While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance.

<<roc-code, fig.width = 5, fig.height = 5, out.width = ".5\\textwidth", fig.cap = "ROC curve showing overall model performance.", fig.scap = "Overall model performance ROC curve.">>=
library(pROC)
pred_df <- as_tibble(preds) %>% gather(key = feature, value = value)
test_labs_df <- as_tibble(test_labs) %>% gather(key = feature, value = value)
whole_model_roc <- roc(test_labs_df$value, pred_df$value)

@@

<<auc-code, fig.width = 8, fig.height = 6, out.width = "\\textwidth", fig.cap = "Class-by-class ROC curves. AUC is area under the curve, a measure of overall model performance. Equal error rates are marked, indicating the position at which there is equal probability of a false positive or false negative error.", fig.scap = "Class-by-class ROC curves.">>=
aucs <- plot_onehot_roc(preds, test_labs, str_to_title(classes))
thresholds <- purrr::map_dbl(aucs$data$eer, ~.$thresholds)
aucs$data$thresholds <- thresholds

@@

Although some efforts to generalize confusion matrices to multi-class problems do exist in the literature \citep{landgrebeEfficientMulticlassROC2008}, it appears that confusion matrices have not previously been applied to multi-label classification problems. Since a single image may belong to a combination of the $n$ categories, it is no longer true that a false positive and a false negative are equivalent (see \autoref{tab:error-3class-problem}). The confusion matrix presented in \autoref{fig:confusion_matrix} is like a traditional confusion matrix in that all values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values, however, are adjusted from the traditional method to remove the effect of any true positives from the calculation of false positive proportions. For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels.

@@

\autoref{fig:confusion_matrix} shows the general weaknesses of the model, but does not necessarily suggest where to look as to \emph{why} the model is not performing appropriately. %In Sections~\ref{sec:model-consistency} and \ref{sec:heatmap}, alternative visualizations are used to better understand the weaknesses of the model when applied to actual images used to train, test, and validate the model.

>>>>

<<>>=
img_names <- dfunion$filename %>% basename() %>% as.vector

labs <- sapply(classes, grepl, x = str_extract(img_names, "^.*?-\\d?-"))
str <- gsub("^.*?-\\d{0,2}-", "", img_names)

# Extract first, first two, and first three words of string
brand_1 <- str_extract(str, "^.*?-")
brand_2 <- str_extract(str, "^.*?-.*?-")
brand_3 <- str_extract(str, "^.*?-.*?-.*?-")

# These are the beginning of brands that need an extra word extracted
multi_brands <- c("the", "the-north", "polo", "polo-ralph", "5", "5-11",
                  "1", "to", "dr", "la", "new", "old", "under",
                  "steve", "bernie", "cole", "tory",
                  "harley", "kristin", "eric",
                  "spring", "chinese", "dirty")

brand <- ifelse(brand_1 %in% paste0(multi_brands, "-"),
                ifelse(brand_2 %in% paste0(multi_brands, "-"),
                       brand_3, brand_2),
                brand_1) %>%
  gsub(. , pattern = "-", replacement = " ") %>%
  trimws(., "right"); rm(brand_1, brand_2, brand_3, multi_brands)

df_images <- cbind(tibble(str, brand), labs)

df_shoes <- df_images %>%
  group_by(str, brand) %>%
  summarize_at(vars(bowtie:triangle), any)

top_brands <- df_shoes %>%
  group_by(brand) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

df_summ <- filter(df_shoes, brand %in% head(top_brands$brand, 8)) %>%
  group_by(brand) %>%
  summarize(n = n(),
            bowtie = sum(bowtie)/n, chevron = sum(chevron)/n,
            circle = sum(circle)/n, line = sum(line)/n,
            polygon = sum(polygon)/n, quad = sum(quad)/n,
            star = sum(star)/n, text = sum(text)/n, triangle = sum(triangle)/n)

df_summ_long <- df_summ %>%
  gather(key = shape, value = prop, -brand, -n) %>%
  arrange(brand)

df_summ_long$brand <- as.factor(df_summ_long$brand)
df_summ_long$shape <- factor(df_summ_long$shape, levels = classes)

# Line plot
ggplot(df_summ_long) + geom_point(aes(x = prop, y = shape, color = brand)) +
  geom_path(aes(x = prop, y = shape, group = brand, color = brand)) +
  ggtitle("Shape proportions by brand")

# unicode_symbols <- c(bowtie = "\u26FB", chevron = "\uFE3D",
#                      circle =  "\u23FA", line = "\u2225",
#                      polygon = "\u2B23", quad = "\u25A0",
#                      star = "\u2605", text = "a", triangle = "\u25BC",
#                      other = "\u003F")

ggplot(df_summ_long, aes(x = brand, y = prop, shape = factor(shape),
                         color = factor(shape))) +
  geom_point(size = 4) +
  scale_shape_manual(values = c("\u26FB","\uFE3D","\u23FA","\u2225",
                                "\u2B23","\u25A0","\u2605","a","\u25BC")) +
  theme_bw() +
  coord_flip() +
  ggtitle("Proportion of labeled shoes containing each shape by brand")
@

@@

\paragraph{Overall Accuracy} % Model-wise and class-by-class, w/ confusion matrix
\svp{You need to explain these terms. Your CC was written for statisticians, this paper is for practitioners. You need a MUCH gentler introduction to the idea of accuracy, errors, and ROC curves, as well as a lot more definitions for terms.}
\autoref{fig:overall-roc} shows the ROC curve for the full model, and \autoref{fig:class-roc} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for line) to 0.91 (for bowtie and text). While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance.

<<overall-roc, fig.width = 5, fig.height = 5, out.width = ".5\\textwidth", fig.cap = "ROC curve showing overall model performance.", fig.scap = "Overall model performance ROC curve.">>=
library(pROC)
pred_df <- as_tibble(preds) %>% gather(key = feature, value = value)
test_labs_df <- as_tibble(test_labs) %>% gather(key = feature, value = value)
whole_model_roc <- roc(test_labs_df$value, pred_df$value)

@@

<<class-roc, fig.width = 8, fig.height = 6, out.width = "\\textwidth", fig.cap = "Class-by-class ROC curves. AUC is area under the curve, a measure of overall model performance. Equal error rates are marked, indicating the position at which there is equal probability of a false positive or false negative error.", fig.scap = "Class-by-class ROC curves.">>=
aucs <- plot_onehot_roc(preds, test_labs, str_to_title(classes))
thresholds <- purrr::map_dbl(aucs$data$eer, ~.$thresholds)
aucs$data$thresholds <- thresholds

@@

Although some efforts to generalize confusion matrices to multi-class problems do exist in the literature \citep{landgrebeEfficientMulticlassROC2008}, it appears that confusion matrices have not previously been applied to multi-label classification problems. Since a single image may belong to a combination of the $n$ categories, it is no longer true that a false positive and a false negative are equivalent. In the confusion matrix presented in \autoref{fig:confusion_matrix}, the values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, the values are adjusted to remove the effect of any true positives from the calculation of false positive proportions. For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels.

@@

\autoref{fig:confusion_matrix} shows the general weaknesses of the model, but does not necessarily suggest where to look as to \emph{why} the model is not performing appropriately.
